Improving the Accuracy of a Sequential Mining Model for Hurricane Trajectory Prediction

### 2018-02-05 paper/manuscript_revised.tex
minor fixes

Section (2) of AprioriAll is responsible for the generation of frequent sequences. In the case of hurricane trajectory prediction, these sequences correspond to frequently recorded hurricane coordinate sequences. Frequent hurricane coordinate sequences are those which have a support (occurance count) greater than or equal to the \textit{minimum support}. In general terms, the sequence generation step of AprioriAll develops frequent ordered patterns of increasing length, beginning with frequent single-item sequences (corresponding to frequent single-point sequences). This step begins by scanning the $\langle HurricaneID, CoordinateSequence\rangle$ database for frequent single-point trajectories. The frequent single-point trajectories are then converted to candidate two-point trajectories by an inner join. The candidate two-point trajectories are scanned against the database to determine which candidates satisfy the minimum support. Running an inner join against the frequent k-point trajectories generates the candidate (k+1)-point trajectories. Once the sequence generation level reaches 3, each candidate sequence must be pruned if any of their subsequences are infrequent. The complete exectuion of AprioriAll results in a collection of all frequent hurricane trajectory patterns defined by the minimum support.

@@

% H is in RADS, Eucl in degrees
Where $\Delta Lat$ and $\Delta Lon$ respectively denote the differences in latitude and longitude between points q and p. Note that the Euclidean distance formula expresses Latitude and Longitude in degrees and minutes, while the Haversine formula expresses Latitude and Longitude exclusively in radians. In addition, whereas the Euclidean formula expresses distance in terms of units on a plane, the Haversine formula expresses distance in terms of portions of a single unit sphere. Therefore, to express distance in kilometres, the result of Haversine formula must be multiplied by R, which denotes the radius of the earth in kilometres (approximately 6371km \cite{earth-radius-kilometres}).

>>>>

Section (2) of AprioriAll is responsible for the generation of frequent sequences. In the case of hurricane trajectory prediction, these sequences correspond to frequently recorded hurricane coordinate sequences. Frequent hurricane coordinate sequences are those which have a support (occurrence count) greater than or equal to the \textit{minimum support}. In general terms, the sequence generation step of AprioriAll develops frequent ordered patterns of increasing length, beginning with frequent single-item sequences (corresponding to frequent single-point sequences). This step begins by scanning the $\langle HurricaneID, CoordinateSequence\rangle$ database for frequent single-point trajectories. The frequent single-point trajectories are then converted to candidate two-point trajectories by an inner join. The candidate two-point trajectories are scanned against the database to determine which candidates satisfy the minimum support. Running an inner join against the frequent k-point trajectories generates the candidate (k+1)-point trajectories. Once the sequence generation level reaches 3, each candidate sequence must be pruned if any of their subsequences are infrequent. The complete execution of AprioriAll results in a collection of all frequent hurricane trajectory patterns defined by the minimum support.

@@

Where $\Delta Lat$ and $\Delta Lon$ respectively denote the differences in latitude and longitude between points q and p. Note that the Euclidean distance formula expresses Latitude and Longitude in degrees and minutes, while the Haversine formula expresses Latitude and Longitude exclusively in radians. In addition, whereas the Euclidean formula expresses distance in terms of units on a plane, the Haversine formula expresses distance in terms of portions of a single unit sphere. Therefore, to express distance in kilometres, the result of Haversine formula must be multiplied by R, which denotes the radius of the earth in kilometres (approximately 6371km \cite{earth-radius-kilometres}).
